### 2017-07-17 background.tex
Whitespace cleanup
Adding a new cite

\kyle{Any citations for the following}
Formal privacy techniques such as homomorphic encryption, secure multiparty computation, and
other cryptographic solutions for protecting private data often require significant computational
overhead~\cite{naehrig2011can}. Prior work on database based solutions \cite{popa2011cryptdb}
demonstrates the need for matching the privacy protecting methods used to the analysis in question
to reduce overheads. The majority of the work in this area is focused on the security of
numerical data, while the data we are dealing with is mostly large volumes of textual data.
Recent approaches for applying privacy techniques to securely compute
mathematical operations at large scale incur a 2x overhead~\cite{kepner2014computing}.

>>>>

\kyle{Any citations for the following}
Formal privacy techniques such as homomorphic encryption, secure multiparty computation, and
other cryptographic solutions for protecting private data often require significant computational
overhead ~\cite{gentry2012fully} \cite{naehrig2011can}. Prior work on database based solutions \cite{popa2011cryptdb}
demonstrates the need for matching the privacy protecting methods used to the analysis in question
to reduce overheads. The majority of the work in this area is focused on the security of
numerical data, while the data we are dealing with is mostly large volumes of textual data.
Recent approaches for applying privacy techniques to securely compute
mathematical operations at large scale incur a 2x overhead~\cite{kepner2014computing}.
